Extracting Information from AGN Variability

### 2017-03-22 Manuscript.tex
Soften Line 168
Line 168 has been softened to indicate that we only suggest that the
Green's function is a powerful probe.

We propose a Green's function-based method for analysing observed light curves, particularly in the UV through IR where the fluctuations are smaller than they tend to be in the X-ray. Such a method facilitates comparison with analytic and simulation work on variability. Our method builds on the C-ARMA modelling technique of \citet{Kelly14} by proposing that the C-ARMA process is a direct result of the physics driving the variability.

>>>>

We propose a Green's function-based method for analysing observed light curves, particularly in the UV through IR where the fluctuations are smaller than they tend to be in the X-ray. Such a method facilitates comparison with analytic and simulation work on variability. Our method builds on the C-ARMA modelling technique of \citet{Kelly14} by proposing that the Green's Function of the LHS of the C-ARMA process is a powerful probe of the physics driving the variability.
